---
title: "10-ggplot2"
author: "Jameel Alsalam"
date: "May 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ggplot2

ggplot2 is a package -- it's name stands for the "grammar of graphics" which is a principled approach to constructing graphics using a translation of data into different plot layers and visual marks. While it is not the only way to plot in R, it is a great way to learn!

```{r pkgload}
library("tidyverse")
```

Press the "play" button at the right of the code block above to load the tidyverse packages (which includes ggplot2)

Let's follow along in [R for Data Science](http://r4ds.had.co.nz/data-visualisation.html)

`mpg` is a dataset included in the ggplot2 package which has data on the fuel economy of various cars. It is often used as an example dataset.

```{r}
mpg
```


You can type "ctrl-alt-i" to insert a new code chunk in an Rmarkdown document.

The R4DS chapter starts with a question -- do you think that cars with big engines use more fuel than cars with small engines? What is the relationship of these variables.

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))

```

Discuss the major elements here:
1. ggplot() function starts it all
2. data argument defines the data that we are plotting (it all should be in one data frame)
3. a geom function to translate the data into marks using a mapping


Try the first set of exercises at 3.2.4 in http://r4ds.had.co.nz/data-visualisation.html


A code chunk you can use to get started here:

```{r}




```

Feel free to write notes to yourself (you no longer have to # comments) and insert more code chunks either by typing triple backtick open-brace, or with ctrl-alt-i.

















You might be interested to know that the book "R for Data Science" is actually written as a series of Rmarkdown files which are then "knit" to make both the web html form of the book and to pdf for the print form of the book.

Check out the visualize chapter of [r4ds on Github](https://github.com/hadley/r4ds/blob/master/visualize.Rmd)

You might notice that all the text is the same, but there are no plots -- instead there is the code that generates the plots.
